---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# zddr

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/jordagaman/zddr.svg?branch=main)](https://travis-ci.com/jordagaman/zddr)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/jordagaman/zddr/workflows/R-CMD-check/badge.svg)](https://github.com/jordagaman/zddr/actions)
[![Codecov test coverage](https://codecov.io/gh/jordagaman/zddr/branch/main/graph/badge.svg)](https://codecov.io/gh/jordagaman/zddr?branch=main)
<!-- badges: end -->

The goal of `zddr` is to enable definition, manipulation, and solving of fault 
tree problems using an implementation of 
[zero-suppressed binary decision diagram](https://en.wikipedia.org/wiki/Zero-suppressed_decision_diagram) 
algorithms in R.

## Installation

<!--
You can install the released version of zddr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("zddr")
```
-->

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jordagaman/zddr")
```
## Example

This is a simple cutset.

```{r example}
library(zddr)
zdd(1) * zdd(2) * zdd(3)
```

You can create the same cutset above with a simpler call:

```{r example2}
zdd_and(1, 2, 3)
```

Multiple cutsets look like this:

```{r example3}
zdd_and(1, 2, 3) | zdd_and(4, 5) | zdd(6)
```


The real magic is ensuring that when you add a new cutset, you check if either 
that one or the existing ones are nonminimal. For example, `{1,2,3}` is
nonminimal to `{1}`. Check this out:

```{r example4}
zdd_and(1, 2, 3) | zdd_and(4, 5) | zdd(6) | zdd(1)
```


## Longer-term vision

This package is in a developmental state. The ultimate dream is to simplify the
user interface using the increasingly robust `as_zdd()` function. 

The most basic use of `as_zdd()` accepts numeric and integer inputs.
```{r aszdd_integer}
as_zdd(10)
as_zdd(10L)
```

The function also assumes that vectors are meant to represent a cutset.

```{r aszdd_vector}
as_zdd( c(1,2,3) )
```

And lists are meant to represent a collection of cutsets.

```{r aszdd_list}
as_zdd( list(1,2,3) )
```

One can combine the two to produce a ZDD representation of cutsets. The final 
example from the last section is reproduced here using only base R types and the
`as_zdd()` function.

```{r aszdd_cutsets}
lst <- list(
  c(1,2,3),
  c(4,5),
  6,
  1
)
as_zdd(lst)
```

There are two effects to the above. First, it enables a complete round trip
between base R cutsets and ZDDs.

```{r roundtrip}
z <- as_zdd(lst)
cutsets(z)
cutsets( as_zdd(cutsets(z)) )
```

Second, it enables quick generation and then manipulation of ZDDs without having
to know too much about the internals of the `zddr` implementation.

```{r manip}
z * list(1, c(2,3), 4)
```
