---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# zddr

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/jordagaman/zddr.svg?branch=main)](https://travis-ci.com/jordagaman/zddr)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/jordagaman/zddr/workflows/R-CMD-check/badge.svg)](https://github.com/jordagaman/zddr/actions)
[![Codecov test coverage](https://codecov.io/gh/jordagaman/zddr/branch/master/graph/badge.svg)](https://codecov.io/gh/jordagaman/zddr?branch=master)
<!-- badges: end -->

The goal of zddr is to ...

## Installation

You can install the released version of zddr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("zddr")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jordagaman/zddr")
```
## Example

This is a simple cutset.

```{r example}
library(zddr)
zdd(1) * zdd(2) * zdd(3)
```

You can create the same cutset above with a simpler call:

```{r example2}
library(zddr)
zdd_and(1, 2, 3)
```

Multiple cutsets look like this:

```{r example3}
library(zddr)
zdd_and(1, 2, 3) | zdd_and(4, 5) | zdd(6)
```


The real magic is ensuring that when you add a new cutset, you check if either 
that one or the existing ones are nonminimal. For example, {1,2,3} is
nonminimal to {1}. Check this out:

```{r example4}
library(zddr)
zdd_and(1, 2, 3) | zdd_and(4, 5) | zdd(6) | zdd(1)
```
