---
title: "Using Symbols instead of Variable Order Integers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using Symbols instead of Variable Order Integers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(zddr)
```

```{r silent, echo=FALSE, message=FALSE, results='hide'}
zdd0()
```

Currently, the `zddr` package only works using integer variables corresponding
to variable rank. An additional layer of abstraction is needed for the user to
enter real life fault tree problems, which can be converted to the integer
variable form for solving.

The purpose of this vignette is to use the existing `zddr` package for a fault
tree problem to discover the design of functions that will do this 
automatically. This vignette will be retired once the `zddr` package exposes
the new symbolic functions. Easy enough.

## Define a problem

Imagine a system with four trains: A, B, C, and D. The fault tree of the first
train is essentially an OR gate of the following subtrees:

* Failures of Train A that have no dependencies to the other trains: 
  `IND_A`
* Failures of Train A that have dependencies with one other train: 
  `CCF_AB`, `CCF_AC`, `CCF_AD`
* Failures of Train A that have dependencies with two other trains:
  `CCF_ABC`, `CCF_ABD`, `CCF_ACD`
* Failures of Train A that have dependencies with all trains:
  `CCF_ABCD`

## Set up variables

For a complete description of the problem, the entire range of possible 
variables are assigned integers. (Remember: doing this the long way right now to
help discover what the clever functions will be. This will be necessarily 
painful.)

```{r variables}
# independent failures
IND_A    <-  1;   IND_B    <-  2;   IND_C    <-  3;   IND_D    <-  4
# dependencies between two trains
CCF_AB   <-  5;   CCF_AC   <-  6;   CCF_AD   <-  7
CCF_BC   <-  8;   CCF_BD   <-  9;   CCF_CD   <- 10
# dependencies between three trains
CCF_ABC  <- 11;   CCF_ABD  <- 12;   CCF_ACD  <- 13;   CCF_BCD  <- 14
# dependencies between all trains
CCF_ABCD <- 15
```

## Use `zddr` to create simple system trees

With the variables defined, the train failure cutsets can be given by the 
following OR gates for each train.

```{r train_failures}
A <- zdd_or(IND_A, CCF_AB, CCF_AC, CCF_AD, CCF_ABC, CCF_ABD, CCF_ACD, CCF_ABCD)
B <- zdd_or(IND_B, CCF_AB, CCF_BC, CCF_BD, CCF_ABC, CCF_ABD, CCF_BCD, CCF_ABCD)
C <- zdd_or(IND_C, CCF_AC, CCF_BC, CCF_CD, CCF_ABC, CCF_ACD, CCF_BCD, CCF_ABCD)
D <- zdd_or(IND_D, CCF_AD, CCF_BD, CCF_CD, CCF_ABD, CCF_ACD, CCF_BCD, CCF_ABCD)
```

```{r train_A}
A
```

Admittedly, the `zddr` package still needs a good way to translate the results
back to the original variable names for better readability. The best way to 
accomplish that translation is part of what this vignette is trying to discover.
Be patient, okay?

## Manipulate the trees

Some examples of tree manipulation follow. Remember, there are four "trees" 
defined above, one for each train. The examples below explore 

### Multiply two trees

What are the cutsets associated with failure of trains A _and_ B? 

```{r A_and_B}
A*B
```

Note that there were common events between `A` and `B`. For this reason
the crossproduct of `A` and `B` has only `r length(cutsets(A*B))` cutsets. If 
this problem were to be solved by brute force cross multiplication, the solution
would have to look at all `r length(cutsets(A))*length(cutsets(B))` combinations
of `A` and `B`'s trees and then filter out the non-minimal cutsets. The full
cross multiplication is trivial for a small problem, but would quickly get 
unmanageable for a problem with many `AND` operations. 

### Multiply three trees

What are the cutsets associated with failure of trains A _and_ B _and_ D?

```{r A_and_B_and_D}
A*B*D
```

As above, there were common events between `A`, `B`, and `D`, resulting in only
`r length(cutsets(A*B*D))` cutsets. This is far fewer than the maximum possible
number of cutsets by brute force cross multiplication,
`r length(cutsets(A))*length(cutsets(B))*length(cutsets(D))`.

### Multiply all four trees

What about failure of all four?

```{r all_four}
A*B*C*D
```

Again, the cross multiplication using `zddr` directly identifies the 
`r length(cutsets(A*B*C*D))` nonminimal cutsets, without having to first 
generate the 
`r length(cutsets(A))*length(cutsets(B))*length(cutsets(C))*length(cutsets(D))`
possible cutsets by brute force. Huzzah!


### k of n train failures

For now, k of n failures is done manually. If we were interested in the list
of cutsets that represents failure of at least 2 trains, it would be the 
logical OR of the AND of all possible pairs of trains. Note how compact the 
results actually are: there are `r 6*8*8` possible combinations of cutsets for 
the problem defined, but the ZDD method quickly filters down to the `r 17` that
match the criteria without evaluating all permutations.

```{r two_of_four}
(A*B) | (A*C) | (A*D) | (B*C) | (B*D) | (C*D)
```

Repeating the same exercise, except with failure of at least 3 trains. Again, 
instead of evaluating `r 3*8*8*8` combinations, the ZDD method quickly 
identifies the `r 32` cutsets that meet the criteria.

```{r three_of_four}
(A*B*C) | (A*C*D) | (B*C*D) 
```

What about _exactly_ 3 failed trains? EASY.

```{r three_of_four_exact}
( (A*B*C) | (A*C*D) | (B*C*D) ) %anot% (A*B*C*D)
```


